Article title

### 2017-06-27 paper-webserver.tex
ADD: third para

Here we present Spfy, a platform for bundling subtyping modules and machine-learning predictions, built using modern containerization of services, task queues for parrelelizing analyses, and exception handling throughout.

>>>>

Here we present Spfy, a platform for bundling subtyping modules and machine-learning predictions, and built using modern containerization of services, task queues for parrelelizing analyses, and exception handling throughout. Spfy offers serotype prediction, identification of antimicrobial resistance genes through the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and statisical or machine-learning based comparisons of groups based on user-selected restrictions.
